\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 pwarel.tex
.

The abstraction of the hybrid dynamical system is defined by
paritioning the combiend state-input space $\HybridStates \times
\Inputs$ into hyper-rectangles or cells $C_i \in \C$. The cells are
pairwise disjoint $C_i \cap C_j \neq \emptyset$ iff $i \neq j$ and
their union $\bigcup_{C_i\in\C}C_i$ is the state-input
space $\HybridStates \times \Inputs$. This discrete abstraction over
the continuous space is implicit and defined using a quantization
function $Q_\epsilon$ parameterized by the precision $\epsilon$.
This further defines an equivalence relations such that
\[
    (\vx_i, \vu_i) \equiv (\vx_j, \vu_j) \;\text{iff}\; Q()
\]

$(\vx_i, \vu_i) \in C_i \; \text{iff} \; \C_i = Q(\vx_i, \vu_i)$

\begin{definition}[] Let C be a d-quantized tiling. The d-quantized
    tiling-based plant abstraction (denoted Pd) is given by a graph
    (V, E), where V = C, and the set of edges E is defined such that
    (Cj, Ck) ∈ E iff: there is a state-input pair (x, u) ∈ Cj and a
state-input pair (x 0 , u) ∈ Ck such that x 0 = SIM(x, u, τ ).
\end{definition}

@@

\begin{definition}[Abstract State Graph]. Let ∆ > 0 be a fixed time
    step. The abstract state graph H(∆) for time step ∆ is defined by
    the set of vertices C, and edges (Ci, Cj ) whenever Ci ∆ Cj . Let
    C0 denote the collection of initial cells in C, i.e., cells Ci
    such that Ci ∩ X0 6= ∅. Further, let Cu denote the set of unsafe
    cells, or cells Cj such that there is a state xj ∈ Cj that reaches
    an unsafe state y ∈ Xf within time 0 ≤ tj < ∆. The abstraction
H(∆) is given by D C, ∆ , C0, Cu E .  \end{definition}

>>>>

The abstraction of the hybrid dynamical system is defined by
paritioning the combiend state-input space $\HybridStates \times
\Inputs$ into hyper-rectangles or cells $C_i \in \C$. The cells are
pairwise disjoint $C_i \cap C_j \neq \emptyset$ iff $i \neq j$ and
their union $\bigcup_{C_i\in\C}C_i$ is the state-input
space $\HybridStates \times \Inputs$. This discrete abstraction over
the continuous space is implicit and defined using a quantization
function $Q_\epsilon$ parameterized by the precision $\epsilon$.
This further defines an equivalence relations such that
\[
    (\vx_i, \vu_i) \equiv (\vx_j, \vu_j) \;\text{iff}\; Q_\epsilon(\vx_i,
    \vu_i) = Q_\epsilon(\vx_j, \vu_j)
\]
In other words, $(\vx_i, \vu_i) \in C_i \; \text{iff} \; C_i =
Q_\epsilon(\vx_i, \vu_i)$.

\begin{definition}[Graph Abstraction]
    The quantization function $Q_\epsilon$ induces a DAG on the discrete
    abstraction given by a graph $G(V, E)$, where each vertex
    corresponds to a cell $V_i = C_i$, and an edge exists between two
    cells $(C_j, C_k) \in E$ iff there exist state-input pairs
    $(\vx,\vu) \in C_j$, $(\vx', \vu) \in C_k$ such that $\vx =
    \simulate(\vx, \vu )$.
\end{definition}

@@

% \begin{definition}[Abstract State Graph]. Let ∆ > 0 be a fixed time
%     step. The abstract state graph H(∆) for time step ∆ is defined by
%     the set of vertices C, and edges (Ci, Cj ) whenever Ci ∆ Cj . Let
%     C0 denote the collection of initial cells in C, i.e., cells Ci
%     such that Ci ∩ X0 6= ∅. Further, let Cu denote the set of unsafe
%     cells, or cells Cj such that there is a state xj ∈ Cj that reaches
%     an unsafe state y ∈ Xf within time 0 ≤ tj < ∆. The abstraction
% H(∆) is given by D C, ∆ , C0, Cu E .  \end{definition}
